\documentclass{llncs}

%\pagestyle{plain}
\usepackage{bibnames}
\usepackage{booktabs} % For formal tables
\usepackage{caption}
\usepackage[caption=false]{subfig}
%\usepackage{subcaption}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}


\newcommand{\myfootnote}[1]{
    \renewcommand{\thefootnote}{}
    \footnotetext{\scriptsize#1}
    \renewcommand{\thefootnote}{\arabic{footnote}}
}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  language=C,
  basicstyle=\scriptsize\ttfamily,
  %basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=[1]\color{blue},       % keyword style
  keywordstyle=[2]\color{mymauve},       % keyword style
  morekeywords=[2]{*, },            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=1,                       % sets default tabsize to 2 spaces
  title=\lstname,                   % show the filename of files included with \lstinputlisting; also try caption instead of title
  xleftmargin=10pt,
}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\newcommand{\tanN}[1] {{\color{red}{TanN}}: {\color{red}{#1}}}
\newcommand{\cyC}[1] {{\color{green}{CyC}}: {\color{green}{#1}}}
\newcommand{\johnB}[1] {{\color{blue}{JohnB}}: {\color{blue}{#1}}}
\newcommand{\bryceL}[1] {{\color{cyan}{BryceL}}: {\color{cyan}{#1}}}
\newcommand{\samW}[1] {{\color{violet}{SamW}}: {\color{violet}{#1}}}
\newcommand{\johnS}[1] {{\color{orange}{JohnS}}: {\color{organe}{#1}}}
\newcommand{\daveD}[1] {{\color{purple}{DaveD}}: {\color{purple}{#1}}}

\begin{document}
\title{A DAG-based Programming Tool For Highly Efficient Codes on Accelerators}

\author{
Tan Nguyen,
John Bachan,
Bryce Lelbach,
Samuel Williams,
John Shalf,\\
David Donofrio, and Cy Chan}
\institute{Lawrence Berkeley National Laboratory, USA\myfootnote{Email: tannguyen@lbl.gov. Bryce Lelbach recently moved to NVIDIA.}
}

\maketitle

\begin{abstract}
Recently, heterogeneous architectures have gained traction in HPC. 
Systems with deep and complex hardware hierarchy and equipped with accelerators each having thousands of cores are increasingly commonplace. 
Optimizing application codes for scalability on such hardware design is extremely challenging, since it requires effective management of the massive thread pool and the ability to balance the workload and hide communication cost among threads/accelerators.
To alleviate these labor intensive jobs, we present a solution based on task parallelism, abstracting away many hardware details associated with sophisticated accelerator architectures such as GPUs. 
We also develop a runtime system called RambutanAcc that can schedule coarse and fine-grain tasks on NVIDIA's GPUs.
Using two HPC benchmarks, we demonstrate the effectiveness of our tool without intrusively modifying the source code.
\end{abstract}


\section{Introduction}
\label{sec:intro}
\input{intro}

\section{Heterogeneous Node - a Notable Design Trend}
\label{sec:motivation}
\input{motivation}

\section{Programming Model}
\label{sec:model}
\input{model}

\section{Implementation}
\label{sec:impl}
\input{impl}


\section{Experimental Results}
\label{sec:results}
\input{results}

\section{Related work}
\label{sec:related}
\input{related}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

\section*{Acknowledgments}
This material is based upon work supported by the Advanced Scientific Computing Research Program in the U.S. Department of Energy, Office of Science, under  Award Number DE-AC02-05CH11231.
RambutanAcc and application codes were developed on TiDA, a workstation housed at LBNL, with GPUs provided by NVIDIA.
We would like to thank Paul Hargrove for his great help on GASNet.

%\input{artifact}

\bibliographystyle{splncs03}
\bibliography{ref} 


\end{document}
